\sys: Automated Data-Parallel Shell Processing

### 2020-04-12 pldi/draft.tex
A hypothesis that might explain our results

>>>>

\kk{Hypothesis on results. Dish gives a great speedup if one step of
  the pipeline is what takes the most time. If the pipeline is long
  with many computation heavy tasks, task based parallelism gets you
  part of the way there, so we can't expect Dish to give performance
  benefits equal to the amount of parallelism that we give it.}
